Learning Augmented Joint-Space Task-Oriented Dynamical Systems: \\ A Linear Parameter Varying and Synergetic Control Approach

### 2017-10-18 paper/main_RA-L_v1.tex
Latest changes in paper
Latest changes

\begin{abstract}
\textcolor{red}{Too long, re-write}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space with respect to the robot's kinematic constraints. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, we prove that it stably moves towards its target and is guaranteed to obey the robot's kinematic joint limits. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system, enabling us to encode complex joint-space behaviors. We propose a method to train such complex behaviors from kinesthetic demonstrations, by learning the parameters of the LPV system. We begin by applying a latent-embedding and a probabilistic approach to discover and represent a set of local behaviors from the demonstrated motions. Then, the corresponding local joint-space behaviors are estimated by solving a convex semi-definite optimization problem that minimizes the joint velocity error from the demonstrations. Our proposed approach is validated on a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 14.0cm},clip]{Without_Obstcle.jpg}
\includegraphics[scale=.23,trim={0 0 0 9.cm},clip]{With_Obstcle.jpg}
\caption{Two robot motions in joint-space accomplishing the same behavior in task-space (pouring chips in a bowl). Though the \textcolor{cyan}{\textbf{task-space trajectories}} are \textit{similar}, the \textcolor{orange}{\textbf{joint-space trajectories}} are different; e.g. the bottom example moves in joint-space to avoid an obstacle that the top one does not.}
\label{fig:robot_example}
\vspace{-0.6cm}
\end{figure}

>>>>

\begin{abstract}
\textcolor{red}{Too long, re-write --}
In this paper, we propose a stable joint-space dynamical system that captures desired behaviors in joint-space while converging towards a reachable target in task-space with respect to the robot's kinematic constraints. Our method is fast to compute and smoothly moves through classic kinematic singularities by avoiding the use of the pseudo-inverse Jacobian; moreover, we prove that it stably moves towards its target and is guaranteed to obey the robot's kinematic joint limits. To encode complex joint-space behaviors while meeting these stability criteria, the dynamical system is constructed as a Linear Parameter Varying (LPV) system, enabling us to encode complex joint-space behaviors. We propose a method to train such complex behaviors from kinesthetic demonstrations, by learning the parameters of the LPV system. We begin by applying a latent-embedding and a probabilistic approach to discover and represent a set of local behaviors from the demonstrated motions. Then, the corresponding local joint-space behaviors are estimated by solving a convex semi-definite optimization problem that minimizes the joint velocity error from the demonstrations. Our proposed approach is validated on a variety of motions for a 7-DOF KUKA LWR4+ robot arm.\end{abstract}

@@

\begin{figure}[t]
\centering
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{Without_Obstcle_white_new.png}
\includegraphics[scale=.23,trim={0 0 0 0cm},clip]{With_Obstcle.png}
\caption{Two robot motions in \textcolor{orange}{\textbf{joint-space}} accomplishing \textit{similar} behavior in \textcolor{cyan}{\textbf{task-space}} (pouring chips in a bowl). The bottom example avoids a known obstacle in its workspace, while the top one does not.}
\label{fig:robot_example}
\vspace{-10pt}
\end{figure}
